\chapter{Defining the general use cases}

\section{Supplantive or generative}

The first important design choice which has to be made is whether the students are supplied with a concept map or flashcards, or that they generate the content themselves. The dichotomy of generative versus supplantive instruction is described in further detail by \citeA{instructionaldesign}, where the implications of both sides are enlisted for the learner, the task and the context.

One of the aspects of generative strategies is that the learner requires a higher amount of prior knowledge, a higher aptitude, and a wider and more flexible range of cognitive strategies, because the content still has to be (partly) researched and constructed. This can be a disadvantage, because the learner might not possess these skills and therefore the instruction may not be suitable or highly inefficient using generative strategies. On the other hand, greater mental effort generally leads to greater depth of processing and therefore better, more meaningful learning, which was also stressed by \citeA{canas} and \citeA{nesbit}. Furthermore, learners experience a higher motivation and a lower amount of anxiety when using generative strategies, and their attribution of success is internal rather than external. 

Furthermore, when using more generative strategies, the learning task becomes more complex and ill-structured, and therefore requires more instruction and time to complete. It also leads to a higher focus on cognitive strategies, but less so on the learning goals. These goals can also not become universal, since each student creates their own flashcards or concept map, and therefore decides on their own learning content.

The most important factor for this design choice is feasibility. The teacher already stated that there is only limited time available during the lesson to introduce them to the software, so there is no time for extensive instruction on how to create concept maps, let alone creating the maps within the classroom. Additionally, students do not have much time at home to spend on creating the maps, and it is also known from both interviews with the teacher as literature that they will probably have only a low amount of intrinsic motivation. Finally, when the students have to create their own maps, it cannot be guaranted that they will include the nodes relevant for the goals of the instruction, and might become either to narrow or to extensive in certain branches. The same arguments are valid for letting students create their own flashcards. Therefore, despite of the benefits that a more generative approach may have for the learning process, the content will be supplied to the students instead.

\section{Choice of platform}

The next design decision is centered around the choice of platform or medium going to be used in order to support the learning tool. In the section \nameref{subsec:fcapplication} on page~\pageref{subsec:fcapplication} it is described that students generally prefer to use traditional or written flashcards, despite the many advantages of digital flashcards. However, with the flashmap tool this is not a feasible option, since the tool has to dynamically generate different graphs based on the general concept map and the profile of the students. Of course it would be possible to provide the concept map digitally and the flashcards in written form, however this would introduce an extra variable to the research design. Finally, with written flashcards one can only use rather crude methods for rescheduling the cards, instead of using the more precise algorithms possible within a digital tool.

There are various options for the specific implementation, for example a computer program or an app. Of these options, a web application is the most convenient, since it is accessible for any device with a modern web browser, and immediately stores the usage data on a centralised server so that it is immediately accessible for the researcher. Furthermore, adjustments or fixes can be applied during the research, without all users having to update to the newest version.

For the client, HTML, CSS, and Javascript are used, importing the vis.js library for visualising the concept map dynamically\footnote{\url{http://www.visjs.org/}}. Furthermore, Python is used for the server logic, communicating with the webclient through a websocket using JSON messages. The choice for Python is mainly based on preference by the programmer. Finally, MongoDB was used as a database engine since it stores data in a format very similar to JSON, which is also used by vis.js to represent concept maps.

The server implementation will be further elaborated in the \nameref{ch:server} chapter on page~\pageref{ch:server}, and the client implementation in the \nameref{ch:client} chapter on page~\pageref{ch:client}.

\section{Supported user actions}

The final design decision related to the general ideation of software is deciding which use cases should be supported, which are generally displayed within a UML use case diagram \cite{uml}. For the flashmap software, the use cases are divided in cases related to the registering and login process (see the \nameref{app:loginusecase} appendix on page~\pageref{app:loginusecase}), and the cases related to the main use of the software (see the \nameref{app:mainusecase} appendix on page~\pageref{app:mainusecase}).

When opening the webapplication, the user is first prompted with a login screen. Here, th e user can either enter an already existing username to continue this session, or he can enter a new name in order to register as a new user. When the user is registering as a new user, a form is presented asking for information on gender and birthdate as descriptive information, and asking for the specific code the user received on the informed consent form in order to validate that the user indeed signed this form before partaking in the research (see section \nameref{ch:procedure} on page~\pageref{ch:procedure}). After that, another form will be prompted for the pretest (section \nameref{ch:instrumentation} on page~\pageref{ch:instrumentation}). When the user has met certain criteria, a posttest similar to the pretest will be prompted, followed by a questionnaire and a debriefing text. When none of these criteria are met, the user can access he main use cases.

The main use cases entail requesting items for review, requesting the learning progress, or logging out. When requesting items for review, the user can receive a due or new flashcard or flashmap, depending whether there are any old items due for review and the experimental group the user is in. Alternatively, the user can also be prompted whether a certain section of the instruction material has been read. These prompts take often place at the beginning of a session so that the user does not have to interrupt a session. Furthermore, they prompt two sections ahead of the material currently being learned or reviewed by the user from the flashmap or flashcards in order to guarantee that the user is familiar with the material before learning the items. Finally, the user is prompted to read a section at most once per day. When requesting the learning progress, the user is presented of an overview of what has already been learned and what is still left as either unseen items or items due for review. This provides an indication for the user so that he can estimate how much time he still needs to invest into the software, but also could stimulate the user by seeing the number of new or due items lowering and learned items increasing. Finally, the user can return to the login screen by logging out.

\section{Description of the client server interaction}
